Theories of deliberated choice

### 2023-11-06 simple.tex
Various draft conj about fals

We thus reach a procedure to determine whether a claim is falsifiable.
Given $C$, compute $C^\subseteq$. Find the set $R$ of relations $\allleadstog$ satisfying $\forall O: \restr{\allleadstog}{O} \in C^\subseteq$. The claim $C$ is falsifiable iff $R \subseteq C$.
\begin{corollary}
  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq} \subseteq C$.
\end{corollary}
A relation $\allleadstog$ is observably in $C$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
All relations in $C$ are observably in $C$. The question of falsifiability asks whether the converse holds.
In other words, $C$ is falsifiable iff it includes the relations observably in $C$.
Define that a relation ${\allleadstog} \in {\allleadstos}$ is \emph{obs-compatible} with a set $S$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S$.
Then, the relations observably in $C$ are exactly those obs-compatible with $C^\subseteq \cap \Theta$.
\begin{corollary}
  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)} = C$.
\end{corollary}
\begin{remark}
  The question of falsifiability is whether the set of relations $\allleadstog$ “compatible” with $C^\subseteq \cap \Theta$ equals $C$.
  Compatibility needs to consider the observables, not a subset of it.
  Define $\Theta_1 \subset \Theta$ as the observations that observe only one pair $(i, \hist)$.
  Define $R_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta_1: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)}$.
  Note that $R \subseteq R_1$.
  We know that $C$ is falsifiable iff $R \subseteq C$. Thus, $C$ is not falsifiable implies $C \subsetneq R \subseteq R_1$ thus $C \subsetneq R_1$. But we do not have that $C \subsetneq R_1$ implies $C$ not falsifiable: could have $C \subsetneq R_1$ but still $R = C$.
\end{remark}

\begin{example}
  Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.

@@

\begin{conjecture}
  Each element of $C$ is a forest (here, meaning, an association of each $i$ to a tree, whose nodes are all the triples in the element and related by “the pair in $\allhists × I$ is a close suffix of the pair in the parent”).
  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
\end{conjecture}
\begin{proof}

\end{proof}
TODO continue here. Use example of constant to $p$ and constant to $p'$ with or without the empty argument and singleton $I$ (falsifiable VS not).
\begin{example}
  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.

  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
  The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
\end{example}
\begin{example}
  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \lor (\ar_2) \ileadstog p'}$ is unfalsifiable.

  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \lor (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
  Observe that any $\theta \in \Theta$ satisfy $\theta((\ar_1), i) = \emptyset \lor \theta((\ar_2), i) = \emptyset$, thus, $C^\subseteq \cap \Theta = \Theta$.
  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.

  The same holds if replacing $(\ar_1)$ and $(\ar_2)$ by any $\hist, \hist' \in \allhists$ that are not one a prefix of the other one.

  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
  It yields a smaller set ${C'}^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
  Thus, $C'$ is falsifiable.

  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well (unless trivial):
  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\subseteq \cap \Theta \wsub {C^{\prime\prime}}^\subseteq \cap \Theta$, thus ${C^{\prime\prime}}^\subseteq \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.

  Now consider the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the alternative smaller claim $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
  It yields a smaller set ${C^{(2)}}^\subseteq \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
  Consider any relation $\allleadstog$ that is obs-compatible with ${C^{(2)}}^\subseteq \cap \Theta$. Assume that for some $\hist, i$, $\hist \ileadstog p$. Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$). Conclude that $\allleadstog$ is constant to $p$.
  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C^{(2)}$ is falsifiable.
\end{example}
\begin{remark}
  Intuition (to be explored, TODO) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time). Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
\end{remark}
\begin{example}
  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_2) \ileadstog^2 p'$.
  Consider the claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$. When is it falsifiable considering these two relations?
\end{example}

>>>>

We thus reach a procedure to determine whether a claim is falsifiable.
Given $C$, compute $C^\subseteq$. Find the set $R$ of relations $\allleadstog$ satisfying $\forall O: \restr{\allleadstog}{O} \in C^\subseteq$. The claim $C$ is falsifiable iff $R \subseteq C$.
\begin{corollary}
  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq} \subseteq C$.
\end{corollary}
A relation $\allleadstog$ is observably in $C$ iff $\forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\subseteq$, equivalently, iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)$.
All relations in $C$ are observably in $C$. The question of falsifiability asks whether the converse holds.
In other words, $C$ is falsifiable iff it includes the relations observably in $C$.
Define that a relation ${\allleadstog} \in {\allleadstos}$ is \emph{obs-compatible} with a set $S$ iff $\forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S$.
Then, the relations observably in $C$ are exactly those obs-compatible with $C^\subseteq \cap \Theta$.
\begin{corollary}
  A claim $C$ is falsifiable iff $\set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)} = C$.
\end{corollary}
\begin{remark}
  The question of falsifiability is whether the set of relations $\allleadstog$ “compatible” with $C^\subseteq \cap \Theta$ equals $C$.
  Compatibility needs to consider the observables, not a subset of it.
  Define $\Theta_1 \subset \Theta$ as the observations that observe only one pair $(i, \hist)$.
  Define $R_1 = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta_1: ({\allleadstog} \cap \theta) \in (C^\subseteq \cap \Theta)}$.
  Note that $R \subseteq R_1$.
  We know that $C$ is falsifiable iff $R \subseteq C$. Thus, $C$ is not falsifiable implies $C \subsetneq R \subseteq R_1$ thus $C \subsetneq R_1$. But we do not have that $C \subsetneq R_1$ implies $C$ not falsifiable: could have $C \subsetneq R_1$ but still $R = C$.
\end{remark}
\begin{example}
  Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.

@@

\begin{example}
  \label{ex:cardPart}
  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhists$ with $\hist$ and $\histp$ non prefix related.
  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.

  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog^{q, q'} q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j]^{q, q'} p$.
  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.

  Then, $C_\psi^\wsub \cap \Theta =
    \set{\theta \in \Theta \suchthat \theta(\hist, i) \in \set{\emptyset, p, p'} \land \theta(\histp, i) \in \set{\emptyset, p, p'} \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.
  % and we see that $C_\psi^\wsub \cap \Theta =
  % \set{\theta \in \Theta \suchthat [\theta(\hist, i) = \theta(\histp, i) = \emptyset \lor \theta(\hist, i) \in \set{p, p'} \lor \theta(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \theta(\histpp, j) \in \set{\emptyset, p}}$.

  Any obs-compatible relation has to satisfy $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
  It also must satisfy ${\allleadstog}(\hist, i) \in \set{p, p'}$, for otherwise, with $\theta = \set{(\hist, i, {\allleadstog}(\hist, i))}$, we get $({\allleadstog} \cap \theta) \notin C_\psi^\wsub \cap \Theta$.
  Similarly, it must satisfy ${\allleadstog}(\histp, i) \in \set{p, p'}$.
  % are $\set{{\allleadstog} \in \allleadstos \suchthat [{\allleadstog}(\hist, i) \in \set{p, p'} \lor {\allleadstog}(\histp, i) \in \set{p, p'}] \land \forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p}$, which, given $p \neq p^{\prime\prime} \neq p'$, contains ${\allleadstog^{p, p^{\prime\prime}}}$, contrary to $C_\psi$.
\end{example}

\begin{example}
  Consider any $i$, $\ar_1 ≠ \ar_2 \in \allargs$, $p, p' \in P$.
  The claim $C = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$ is falsifiable.

  We have $C^\subseteq \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p) \land (\theta((\ar_2), i) = \emptyset \lor \theta((\ar_2), i) = p')}$.
  The obs-compatible relations are $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p \land (\ar_2) \ileadstog p'}$.
\end{example}
\begin{example}
  \label{ex:consti2}
  Assume that $\card{I} ≥ 2$.
  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$. Assume that for some $\hist, i$, $\hist \ileadstog p$. Then, pick any $j \neq i$, and observe that by obs-compatibility, for any $\hist'$, $\hist' \ileadstog[j] p$.
  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and any $(\hist^{\prime\prime}, j)$). Conclude that $\allleadstog$ is constant to $p$.
  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
\end{example}
\begin{example}
  \label{ex:consti1}
  Assume that $\card{I} = 1$.
  Consider any $p, p' \in P$ and the constant functions ${\allleadstog^p}$ to $p$ and ${\allleadstog^{p'}}$ to $p'$ and the claim $C = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$.
  We have $C^\wsub \cap \Theta = \set{\theta \suchthat \theta(\theta^{-1}(P)) = \set{p} \lor \theta(\theta^{-1}(P)) = \set{p'}}$.
  Consider any relation $\allleadstog$ that is obs-compatible with $C^\wsub \cap \Theta$. Assume that for some $\hist, i$, $\hist \ileadstog p$. Observe that by obs-compatibility, $\emptyset \ileadstog p$.
  It follows, still by obs-compatibility, that for any $\hist'$, $\hist' \ileadstog p$ (otherwise pick $\theta$ including $(\hist', i)$ and $(\emptyset, i)$). Conclude that $\allleadstog$ is constant to $p$.
  It follows that the obs-compatible relations are $\set{{\allleadstog^p}, {\allleadstog^{p'}}}$, thus, $C$ is falsifiable.
\end{example}
\begin{example}
  \label{ex:constwout0}
  Consider any $p, p' \in P$ and the claim $C = \set{{\allleadstog} \suchthat (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p) \lor (\forall \hist \neq \emptyset, i \in I: \hist \ileadstog p')}$. That claim is falsifiable iff $\card I ≥ 2$ or $\card \allargs = 1$. The proof if so is similar to \cref{ex:consti2}; otherwise, pick any $\ar \in \allargs$ and note that any relation satisfying $(a.*) \ileadstog p$ and $\forall b \neq a: (b.*) \ileadstog p'$ is obs-compatible with $C^\wsub \cap \Theta$ but is not in $C$.
\end{example}
\begin{example}
  \label{ex:unfor}
  Consider any $i$, $\hist, \histp \in \allhists$, $p, p' \in P$ where $\hist$ and $\histp$ are not prefix related.
  The claim $C = \set{{\allleadstog} \suchthat \hist \ileadstog p \lor \histp \ileadstog p'}$ is unfalsifiable.

  We have $C^\wsub \cap \Theta = \set{\theta \suchthat (\theta(\hist, i) = \emptyset \lor \theta(\hist, i) = p) \lor (\theta(\histp, i) = \emptyset \lor \theta(\histp, i) = p')}$.
  Observe that any $\theta \in \Theta$ satisfy $\theta(\hist, i) = \emptyset \lor \theta(\histp, i) = \emptyset$, thus, $C^\wsub \cap \Theta = \Theta$.
  It follows that the obs-compatible relations are $\allleadstos$, which is bigger than $C$.
\end{example}
\begin{example}
  Consider any $i$, $\ar \neq \ar' \in \allargs$, $p, p' \in P$.
  The claim $C = \set{{\allleadstog} \suchthat (\ar) \ileadstog p \lor (\ar') \ileadstog p'}$ is unfalsifiable (per \cref{ex:unfor}).

  Now consider the smaller claim $C' = \set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$ (thus $C' \ssub C$).
  It yields a smaller set ${C'}^\wsub \cap \Theta = \set{\theta \suchthat (\theta((\ar_1), i) = \emptyset \lor \theta((\ar_1), i) = p)}$.
  The obs-compatible relations are the smaller set $\set{{\allleadstog} \suchthat (\ar_1) \ileadstog p}$.
  Thus, $C'$ is falsifiable.

  Note that any claim $C^{\prime\prime}$ bigger than $C$ is unfalsifiable as well, unless trivial:
  from $C \wsub C^{\prime\prime}$, we deduce $\Theta = C^\wsub \cap \Theta \wsub {C^{\prime\prime}}^\wsub \cap \Theta$, thus ${C^{\prime\prime}}^\wsub \cap \Theta = \Theta$ and the obs-compatible relations are $\allleadstos$, which equals $C^{\prime\prime}$ only if $C^{\prime\prime}$ is trivial.

  Now consider the alternative smaller claim of \cref{ex:consti2}, $C^{(2)} = \set{{\allleadstog^p}, {\allleadstog^{p'}}}$ (thus $C^{(2)} \ssub C$).
  It yields a smaller set ${C^{(2)}}^\wsub \cap \Theta$.
\end{example}
\begin{example}
  \label{ex:for}
  Consider any $i$ and $p, p' \in P$.
  The claim $C = \set{{\allleadstog} \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \hist \ileadstog p) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \hist \ileadstog p')}$, namely, all paths of even lengths lead $i$ to $p$ OR all paths of odd lengths or empty lead $i$ to $p'$, is falsifiable.

  Note that $C^\wsub \cap \Theta = \set{\theta \in \Theta \suchthat (\forall \hist: \card{\hist} \in 2\N \implies \theta(\hist) \in \set{\emptyset, p}) \lor (\forall \hist: (\card{\hist} \in 2\N + 1 \lor \hist = \emptyset) \implies \theta(\hist) \in \set{\emptyset, p'})}$.
  Consider any obs-compatible ${\allleadstog}$.
  Assume that $\exists \hist \suchthat \card{\hist} \in 2\N \land \hist \nileadstog p$.
  Pick $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\hist, i, {\ileadstog}(\hist))}$. We have $({\allleadstog} \cap \theta) \in C^\wsub \cap \Theta$, and ${\allleadstog} \cap \theta = \theta$, and from $\theta \in C^\wsub \cap \Theta$ we obtain ${\ileadstog}(\emptyset) = p'$.
  Similarly, using $\theta = \set{(\emptyset, i, {\ileadstog}(\emptyset)), (\histp, j, {\ileadstog[j]}(\histp))}$, we obtain that $\allleadsto$ conforms to the relation in $C$.
\end{example}

\begin{remark}
  \label{rq:closedcomb}
  Being closed-under-combinations (where a combination forms a new relation by union of parts of relations in $C$) is sufficient to be falsifiable, but not necessary, as seen with \cref{ex:consti2}.
\end{remark}

\begin{remark}
  Intuition (to be explored, TODO) is that when $C^\wsub \cap \Theta$ has the covering property, then the obs-compatible relations are easily deduced from the set (something like, just consider compatibility point per point, one singleton observation at a time). Covering is what is used above, something like $\exists i, \hist, \histp$ such that $\forall \hist^{\prime\prime}: [\forall j \neq i: \set{(\hist, i, .), (\histp, j, .)} \in C^\wsub \cap \Theta] \land [\exists j \neq i \suchthat \set{(\hist', i, .), (\hist^{\prime\prime}, j, .)} \in C^\wsub \cap \Theta]$.
\end{remark}

Define the \emph{suffix} relation $R = \set{(\hist, \histp) \in \allhists × \allhists \suchthat \histp = (\hist, .)}$ as the (infinite) tree whose set of nodes is $\allhists$ and which links  argumentative paths to all of their direct suffixes.
Note that a path in such a tree (an increasing sequence of elements in $\allhists$) corresponds to an argumentative path, that is, to an element of $\allhists$.

Any function ${\ileadstog}: \allhists \mapsto P$ can be considered as having this tree as a domain.
% Define a forest as an association of each $i \in I$ to such a tree.
Any relation ${\allleadstog} \in \allleadstos$ can then be viewed as a forest associating each $i \in I$ to a tree labeled by the function ${\ileadstog}$ (see \cref{fig:forest}).

\begin{figure}
  \begin{tikzpicture}[level distance=0.7cm]

    \tikzstyle{treenode}=[execute at begin node=$, execute at end node=$]
    \tikzstyle{treelabel}=[treenode, anchor=west, inner sep=0]
    \tikzstyle{bottomnode}=[execute at begin node=$\scriptstyle, execute at end node=$]
    \tikzstyle{bottomlabel}=[bottomnode, anchor=west, inner sep=0]
    \tikzstyle{tree}=[level 1/.style={sibling distance=3.4cm, every node/.style=treenode},
    level 2/.style={sibling distance=1.6cm, every node/.style=bottomnode},
    level 3/.style={sibling distance=0.7cm, every node/.style=treenode}
    ]
    \newlength{\lhi}
    \setlength{\lhi}{3.5cm}
    \newlength{\lvi}
    \setlength{\lvi}{1.2cm}

    \path node (all) {$\allleadstog$};

    \path (-\lhi, -\lvi) node[anchor=north] (tree1) {\begin{tikzpicture}
        \path[tree] node (root) {$\emptyset$}
        child {
            node (a) {(a)}
            child {
                node (aa) {(aa)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
            child {
                node (ab) {(ab)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
          }
        child {
            node (b) {(b)}
            child {
                node (ba) {(ba)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
            child {
                node (bb) {(bb)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
          }
        ;
        \begin{scope}[style=treelabel]
          \path (root.east) node {\mapsto p};
          \path (a.east) node {\mapsto p'};
          \path (b.east) node {\mapsto p};
        \end{scope}
        \begin{scope}[style=bottomlabel]
          \path (aa.east) node {\mapsto p'};
          \path (ab.east) node {\mapsto p'};
          \path (ba.east) node {\mapsto p'};
          \path (bb.east) node {\mapsto p};
        \end{scope}
      \end{tikzpicture}};
    \path[->] (all) edge node[midway, above] {$i_1$} (tree1.north);

    \path (\lhi, -\lvi) node[anchor=north] (tree2) {\begin{tikzpicture}
        \path[tree] node (root) {$\emptyset$}
        child {
            node (a) {(a)}
            child {
                node (aa) {(aa)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
            child {
                node (ab) {(ab)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
          }
        child {
            node (b) {(b)}
            child {
                node (ba) {(ba)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
            child {
                node (bb) {(bb)}
                child {
                    node {…}
                  }
                child {
                    node {…}
                  }
              }
          }
        ;
        \begin{scope}[style=treelabel]
          \path (root.east) node {\mapsto p};
          \path (a.east) node {\mapsto p};
          \path (b.east) node {\mapsto p'};
        \end{scope}
        \begin{scope}[style=bottomlabel]
          \path (aa.east) node {\mapsto p};
          \path (ab.east) node {\mapsto p'};
          \path (ba.east) node {\mapsto p'};
          \path (bb.east) node {\mapsto p};
        \end{scope}
      \end{tikzpicture}};
    \path[->] (all) edge node[midway, above] {$i_2$} (tree2.north);
  \end{tikzpicture}
  \caption{A forest}
  \label{fig:forest}
\end{figure}

\begin{conjecture}
  $C$ is falsifiable iff exists two compatible paths in two different such forests, for a given $i$, that are not in a single forest, for that $i$, of $C$.
  This seems incorrect; need to be able to build a union relation!
  Prove that it is false with claim "i goes to phi OR i goes to not phi except for empty set going to phi"?
  Actually I need to be able to merge two relations that agree on everything but some part of the tree, in such a way that all paths crossing the boundary must be in $C$, but not the merge.
  TODO caract with singleton $I$.
  % Given a claim $C$, define $S = C^\wsub \cap \Theta$.
  % We have: $\set{\cup_i(\theta_i) \in \allleadstos \suchthat (\theta_i) \in s_S} = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: ({\allleadstog} \cap \theta) \in S}$.
\end{conjecture}
\begin{remark}
  Say that $(r1, o1)$ is determined in $C$ (to $p$) iff all relations in $C$ including $r1$ agree on ${\allleadstog}(o)$ (satisfy ${\allleadstog}(o) = p$).
  Let $C(r, o)$ equal $\set{{\allleadstog}(o) \suchthat {\allleadstog} \in C \land r \in {\allleadstog}}$.

  A claim satisfying, $\forall {\allleadstog} \in C$:
  $\forall r1 = (o1, p1) \in {\allleadstog}$, $\exists o2$ with $o1$ and $o2$ obs-compatible and $(r1, o2)$ determined in $C$ such that $\forall o3: (o2, o3)$ is obs-compatible and $(r2 = (o2, C(r1, o2)), o3)$ is determined in $C$
  %Perhaps can omit $(r1, o2)$ determined. In fact, has to satisfy that these determine only relations in $C$.
  % \[\forall (\hist, i, p) \in {\allleadstog}, \exists (\histp, j, p) \in {\allleadstog} \suchthat \forall (\histpp, k) \in \allhists × I: \set{(\histp, j), (\histpp, k)} \in O\]
  is falsifiable.

  NOPE.
  Need to say that $C$ is a union of disjoint subsets such that each subset $C'$ include all relations that are specified on a subset of observations (and left free on everything else) which satisfy something like the above condition: all points related to a point that is related to all others.
\end{remark}
\begin{theorem}
  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.

  If $\exists R \subseteq I × \allhists$ such that $C$ is determined on $R$ and satisfying $\exists o \in R \suchthat \forall o' \in R: (\set{o, o'} \in \allpriobss)$, then $C$ is falsifiable.
\end{theorem}
\begin{proof}
  Note that as $C$ is closed-under-combinations, this follows from \cref{rq:closedcomb}, but let’s design a more direct proof in hope of weakening the condition.

  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.

  % Pick any $o_1 \in R$.
  % Define $r_1 = (o_1, {\allleadstog}(o_1))$, thus with $r_1 \in {\allleadstog}$.
  Pick some $o \in R$ as in the hypothesis.
  Consider any $o' \in R$.
  As $\set{o, o'} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
  % $\exists {\allleadstog'} \suchthat \restr{\allleadstog}{\set{o, o'}} = \restr{\allleadstog'}{\set{o, o'}}$.
  $\restr{\allleadstog}{\set{o, o'}} \in C^\wsub$.
  Thus, ${\allleadstog}(o') = f(o')$.

  We obtain that $\forall o' \in R: {\allleadstog}(o') = f(o')$, therefore, ${\allleadstog} \in C$.
\end{proof}
\begin{conjecture}[draft]
  Given $R \subseteq I × \allhists$, say that $C$ is determined on $R$ iff
  % $C = \set{\restr{\allleadstog}{R} \cup \restr{\allleadstog}{R'} \suchthat R' \in (I × \allhists) \setminus R}$.
  $\exists f \in P^R \suchthat C = \set{f \cup g \suchthat g \in P^{(I × \allhists) \setminus R}}$.
  Say that $R$ is coverable iff $\exists o_1, …, O_1, … \suchthat \forall o \in O_1: \set{o_1, o} \in \allpriobss \land \forall o \in O_2: \set{o_2, o} \in \allpriobss \land … \land \set{o_i, o_{i + 1}} \in \allpriobss \land \cup O_i = R \land o_i \in R$.

  If $\exists R \subseteq I × \allhists$ coverable and such that $C$ is determined on $R$, then $C$ is falsifiable.
\end{conjecture}
\begin{proof}
  Consider any ${\allleadstog}$ obs-compatible with $C^\wsub \cap \Theta$ and let us prove that ${\allleadstog} \in C$.

  Pick some $o_1 \in R$ as in the hypothesis.
  Consider any $o \in O_1 \cup \set{o_2}$.
  As $\set{o_1, o} \in \allpriobss$ and ${\allleadstog}$ being obs-compatible, we have
  $\restr{\allleadstog}{\set{o_1, o}} \in C^\wsub$.
  As also $o_1, o \in R$, ${\allleadstog}(o) = f(o)$.
  In particular, ${\allleadstog}(o_2) = f(o_2)$.
  Iterate with $o_2$ and $o \in O_2$, and so on.
  We obtain that $\forall o \in R: {\allleadstog}(o) = f(o)$, therefore, ${\allleadstog} \in C$.
\end{proof}
\begin{example}
  Pick $i \in I$ and
  define $o_1 = ((a), i)$,
  $o_2 = (\emptyset, i)$ and
  $o_3 = ((b), i)$.
  Define $R = \set{o_1, o_2, o_3}$.
  Define $f_1, f_2, f_3 \in P^R$ as follows.
  $f_1(o_1) = \phi$,
  $f_1(o_2) = ¬\phi$,
  $f_1(o_3) = \phi$.
  $f_2(o_1) = \phi$,
  $f_2(o_2) = \phi$,
  $f_2(o_3) = ¬\phi$.
  $f_3(o_1) = ¬\phi$,
  $f_3(o_2) = \phi$,
  $f_3(o_3) = \phi$.
  Define $C = \set{f \cup g \suchthat f \in \set{f_1, f_2, f_3} \land g \in P^{(I × \allhists) \setminus R}}$.

  Note that $R$ is covered by $O_1 = \set{o_1}, O_2 = \set{o_2}, O_3 = \set{o_3}$.
  Note that $C$ is determined on $R$.
  Yet, $C$ is not falsifiable.
